Real Time Fluid Simulation \\ \smaller using Smoothed-Particle Hydrodynamics and OpenGL

### 2014-12-11 paper/paper.tex
Added history section

\section{History}
%
something
%

>>>>

\section{History}
%
\hspace{6 pt} Given all the different applications for Smoothed Particle Hydrodynamics (SPH),
it was first used to simulate interstellar phenomena. Conceived in 1977 by Gingold and 
Monaghan was an improvement to the Standard Finite Difference Method, which until their 
breakthrough, was the method to use to simulate astrophysical phenomena. They improved 
on this method by making "use of Lagrangian description of fluid flow which automatically 
focuses attention on fluid elements" \cite{sphastrophysics}. In this implementation, particles 
"move according to the Newtonian equations with forces due to the pressure gradient and 
other body forces: gravity, rotation and magnetic" \cite{sphastrophysics}.
\\
\hspace*{6 pt} 
%
